### 2018-03-31 paper/sexSelectionSpacing-ver1.tex
Edit Spell Definition

I group spells into four periods based on the year of marriage
or year of the previous birth:
1972--1984, 1985--1994, 1995--2004, and 2005--2016.
The periods follow the main changes in availability and legality of 
prenatal sex determination discussed in the Introduction.
The allocation into periods is determined by when conception and therefore 
decisions on sex selection begin, even if no births are observed until 
nine months later.

>>>>

I group spells into four periods based on the year of marriage
or year of the previous birth:
1972--1984, 1985--1994, 1995--2004, and 2005--2016.
The periods follow the main changes in availability and legality of 
prenatal sex determination discussed in the Introduction.
The allocation into periods is determined by when conception and therefore 
decisions on sex selection can begin, even if we do not observe
any births until nine months later.
